Architectures and Open pNets

### 2018-12-19 2018-Arch-pNets/arch-pNets.tex
Arch-pNets paper: added four example formulas satisfied (allegedly) by the Failure Monitor architecture

@@

>>>>

%% CTL
\newcommand{\AG}[1][\ ]{\ensuremath{\mathtt{AG}#1}}
\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{FG}#1}}
\newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
\newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}

@@

\begin{example}
  The architecture in \fig{schema:ArchFailure:BIP} enforces the
  following properties:
  \begin{enumerate}
  \item There is always a possibility to reset the system after a
    failure:
    \begin{equation}
      \label{eq:prop:reset:can}
      \AG (\PortFail \rightarrow \EF \PortReset).
    \end{equation}
  \item Whenever a reset is requested, it will eventually be
    effectuated:
    \begin{equation}
      \label{eq:prop:reset:will}
      \AG (\PortAsk \rightarrow \AF \PortReset).
    \end{equation}
  \item As long as no failure has occured, the $z$ variable of the
    $\NameTimer$ component has the value $\topinterval$:
    \begin{equation}
      \label{eq:prop:z:top}
      \AW[\quad]{(z = T)}{\PortFail} \land\quad
      \AG \bigl(
      \PortReset \rightarrow \AW[]{(z = T)}{\PortFail}
      \bigr).
    \end{equation}
  \item A timeout can only occur within the specified delay after
    a failure:
    \begin{multline}
      \label{eq:prop:to:delay}
      \forall T_0, T_1 \in \sZ,\
      \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
      \\
      \AW[]{\bigl((\PortTO \land \NameTimer.t = T_1) \rightarrow
        (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
      }{
        (\PortReset \lor \PortResume)
      }\Big),
    \end{multline}
    where $T_0$ and $T_1$ are integer parameters.  (The formula
    holds with the universal quantification over $T_0$ and $T_1$
    due to the fact that their individual values only appear in
    the left-hand sides of the two implications.)
  \end{enumerate}
\end{example}
